#MSDS Spring 2018 
##DATA 607 Data Aquisition and Management
####Jiadi Li
####Week 4 Project 1:R Character Manipulation and Date Processing - Chess Tournament Cross Table

1.read lines of data, store lines into two lists based on number of lines for each records.
```{r}
raw.data <- readLines("https://raw.githubusercontent.com/xiaoxiaogao-DD/DATA607-Project1/master/tournamentinfo.txt")

i <- 5
j <- 6
index <- 1
len <- length(raw.data)

first_line <- vector()
second_line <- vector()

while (i < len| j < len)  {
  first_line[index] <- raw.data[i]#store each first line of each record in the list
  i <- i + 3

  second_line[index] <- raw.data[j]#same for each second line
  j <- j + 3
  index <- index + 1
}
```

2.extract Player's Name, Player's State, Total Number of Points and Player's Pre-Rating.
```{r}
library(stringr)

i <- 1
player_number <- vector()
player_name <- vector()
player_state <- vector()
player_point <- vector()
player_prerating <- vector()

while (i <= length(first_line)) {
  player_number[i] <- str_trim(str_sub(first_line[i],4,5),"left")
  player_name[i] <- str_trim(str_sub(first_line[i],8,40),"both")
  player_state[i] <- str_sub(second_line[i],4,5)
  player_point[i] <- as.numeric(str_sub(first_line[i],42,44))
  player_prerating[i] <- as.numeric(str_trim(str_sub(second_line[i],23,26),"left"))
  i <- i + 1
}

head(player_number)
length(player_number)

head(player_name)
length(player_name)

head(player_state)
length(player_state)

head(player_point)
length(player_point)

head(player_prerating)
length(player_prerating)
```

extract player's number of each opponent.
```{r}
i <- 1
opponent_number <- list(0)

while (i <= length(first_line)) {
  game1 <- as.numeric(str_trim(str_sub(first_line[i],51,52),"both"))
  game2 <- as.numeric(str_trim(str_sub(first_line[i],57,58),"both"))
  game3 <- as.numeric(str_trim(str_sub(first_line[i],63,64),"both"))
  game4 <- as.numeric(str_trim(str_sub(first_line[i],69,70),"both"))
  game5 <- as.numeric(str_trim(str_sub(first_line[i],75,76),"both"))
  game6 <- as.numeric(str_trim(str_sub(first_line[i],81,82),"both"))
  game7 <- as.numeric(str_trim(str_sub(first_line[i],87,88),"both"))
  
  opponent_number[[i]] <- c(game1,game2,game3,game4,game5,game6,game7)
  
  i <- i + 1
}

head(opponent_number)
length(opponent_number)
```

3.Create a dataframe
```{r}
Player_raw <- data.frame(player_number,player_name,player_state,player_point,player_prerating)
head(Player_raw)
summary(Player_raw)
Player_raw$player_prerating[55]
```

4.Create the opponent_prerating column 
```{r}
opponent_prerating <- vector()
opponent_length <- 0
opponent_prerating_sum <- 0
i <- 1
j <- 1

while (i <= length(player_number)) {
  while (j <= length(opponent_number[[i]]) ) {
      temp <- opponent_number[[i]]
      if (is.na(temp[j]) == FALSE) {
        opponent_prerating_sum <- opponent_prerating_sum + Player_raw$player_prerating[Player_raw$player_number==temp[j]]
        opponent_length <- opponent_length + 1
      }
      j <- j +1
    }
  if (opponent_length != 0) {
    opponent_prerating[i] <- round((opponent_prerating_sum/opponent_length))
    opponent_prerating_sum <- 0
    opponent_length <- 0
  }
  i <- i + 1
  j <- 1
}

head(opponent_prerating)
```

5.add the opponent_prerating column to Player dataframe so that the final dataframe includes:<br/>
Player's Name, Player's State, Total Number of Points, Player's Pre-Rating, and Average Pre Chess Rating of Opponents
```{r}
Player <- data.frame(Player_raw,opponent_prerating)
head(Player)
```

6.generate a .csv file
```{r}
write.csv(Player,file = "607_Project1_chess_player.csv",row.names = FALSE)
```